### 2018-02-26 paper/sections/1_introduction.tex
paper: minor typos, add acks, shorten to 10pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+, weil:sc2004-dyn-metadata}. But the policies for what data
to evict and when to evict are specific to the application's behavior and the
hardware configuration so a new workload may prove to be a poor match for the
selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. We evaluate a variety of caching
policies using our data management language/policy engine and arrive at a
customized policy that works well for our example application,
ParSplice~\cite{perez:jctc20150parsplice}.

>>>>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs, weil:sc2004-dyn-metadata}. But the policies for what data
to evict and when to evict are specific to the application's behavior and the
hardware configuration so a new workload may prove to be a poor match for the
selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. We evaluate a variety of caching
policies using our data management language/policy engine and arrive at a
customized policy that works well for our example application,
ParSplice~\cite{perez:jctc20150parsplice}.

### 2018-02-26 paper/sections/2_parsplice-keyspace-analysis.tex
paper: minor typos, add acks, shorten to 10pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \includegraphics[width=1\textwidth]{figures/methodology-keyspace.png}\\
    \caption{Keyspace size and shape.
    \label{fig:methodology-keyspace}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=0.975\textwidth]{figures/motivation-regimes.png}\\
    \caption{Key accesses over time.
    \label{fig:motivation-regimes}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=1.05\textwidth]{figures/methodology-keys.png}\\
    \caption{Redundant key accesses.
    \label{fig:methodology-keys}}
  \end{subfigure}
  \caption{Keyspace analysis for ParSplice.
    (a) shows that the keyspace is small but must satisfy many reads. Memory
    usage scales linearly, so we will eventually need more than one node to manage
    segment coordinates for larger jobs. \(\Delta_1\) is the growth rate (see
    Section~\S\ref{sec:delta}).
    (b) shows that key accesses start with many reads to a small set of
    keys and progresses to less reads to a larger set of keys.  The line shows the
    rate that minima values are retrieved from the key-value store (\(y1\));
    points along the bottom show the unique keys accessed in a 1
    second window (\(y2\)). Despite having different
    \(\Delta\)s, the structure of key accesses are similar.
    (c) shows that over time, tasks start accessing a larger set of keys resulting in
    some keys being more popular than others.  Despite different
    \(\Delta\)s, in both runs some keys are \(5\times\) more popular than others.
  }
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \includegraphics[width=1\textwidth]{figures/methodology-keyspace.png}\\
    \caption{Keyspace size and shape.
    \label{fig:methodology-keyspace}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=0.975\textwidth]{figures/motivation-regimes.png}\\
    \caption{Key accesses over time.
    \label{fig:motivation-regimes}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=1.05\textwidth]{figures/methodology-keys.png}\\
    \caption{Redundant key accesses.
    \label{fig:methodology-keys}}
  \end{subfigure}
  \caption{Keyspace analysis for ParSplice.
    (a) shows that the keyspace is small but must satisfy many reads. Memory
    usage scales linearly, so we will eventually need more than one node to manage
    segment coordinates for larger jobs. \(\Delta_1\) is the growth rate (see
    Section~\S\ref{sec:delta}).
    (b) shows that key accesses start with many reads to a small set of
    keys and progresses to less reads to a larger set of keys.  The line shows the
    rate that minima values are retrieved from the key-value store (\(y1\) axis);
    points along the bottom show the unique keys accessed in a 1
    second window (\(y2\) axis). Despite having different
    \(\Delta\)s, the structure of key accesses are similar.
    (c) shows that over time, tasks start accessing a larger set of keys resulting in
    some keys being more popular than others.  Despite different
    \(\Delta\)s, in both runs some keys are \(5\times\) more popular than others.
  }
\end{figure*}

### 2018-02-26 paper/sections/4_dynamic-policies.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: minor typos, add acks, shorten to 10pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload), and
``Dynamic Policy" (sizes cache according to key access patterns). The dynamic
policies saves the most memory without sacrificing performance.
\label{fig:memory-vs-time}}
\end{figure}%

>>>>

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``Default Policy" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload), and
``Dynamic Policy" (sizes cache according to key access patterns). The dynamic
policies save the most memory without sacrificing performance.
\label{fig:memory-vs-time}}
\end{figure}%

### 2018-02-26 paper/sections/6_conclusion.tex
paper: minor typos, add acks, shorten to 10pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Key-value storage organizations for scientific applications is a field gaining
rapid interest. In particular, the analysis of the ParSplice keyspace and the
development of an appropriate scheme for load balancing is a direct response to
a case study for computation caching in scientific
applications~\cite{jenkins:ipdsw17-mochi}. In that work the authors motivated
the need for a flexible load balancing \emph{microservice} to efficiently scale
a memoization microservice. Our work is also heavily influenced by the
Malacology project~\cite{sevilla:eurosys17-malacology} which seeks to provide
fundamental services from within the storage system ({\it e.g.}, consensus) to
the application.  Our plan is to use
MDHIM~\cite{greenberg:hotstorage2015-mdhim} as our back-end key-value store
because it was designed for HPC and has the proper mechanisms for migration
already implemented.

>>>>

The analysis of the ParSplice keyspace and the
development of an appropriate scheme for load balancing is a direct response to
a case study for computation caching in scientific
applications~\cite{jenkins:ipdsw17-mochi}. In that work the authors motivated
the need for a flexible load balancing \emph{microservice} to efficiently scale
a memoization microservice. Our work is also heavily influenced by the
Malacology project~\cite{sevilla:eurosys17-malacology} which seeks to provide
fundamental services from within the storage system ({\it e.g.}, consensus) to
the application.  Our plan is to use
MDHIM~\cite{greenberg:hotstorage2015-mdhim} as our back-end key-value store
because it was designed for HPC and has the proper mechanisms for migration
already implemented.
